\begin{center}
{\Large \bf Abstract}
\vskip 0.5cm
%\hrule
\end{center}




\thispagestyle{empty}
\begin{singlespacing}

We search for supersymmetry in all hadronic final states with proton-proton collision data recorded by the CMS detector at a center-of-mass energy of 13 TeV. We specifically target for pair produced gluinos in the 2015 data that correspond to an integrated luminosity of 2.3 $\rm fb^{-1}$, and using more than five times  data collected during 2016 where we also add stop and other squark pairs to our search. The data are examined in search regions of jet multiplicity, tagged bottom quark jet multiplicity, missing transverse momentum, and the scalar sum of jet transverse momenta. The observed numbers of events in all search regions are found to be consistent with the expectations from standard model processes. Exclusion limits are calculated for simplified supersymmetric models of gluino pair production. Depending on the assumed gluino decay mechanism, and for a massless, weakly interacting, lightest neutralino, lower limits on the gluino mass from 1440 to 1700 GeV are obtained, significantly extending previous limits.

Another search for the pair production of first generation scalar leptoquarks decaying to leptons and jets is presented. The data corresponding to 2.6 $\rm fb^{-1}$ were collected from proton-proton collisions at a center-of-mass energy of 13 TeV. No significant deviation is found with respect to the standard model predictions. Upper limits are set on cross section times branching fraction. 

The increase of instantaneous luminosity for Run II LHC results in a large number of additional proton-proton collisions in a given event (pileup) leading to contamination of jets. We study advanced pileup removal techniques like trimming, prunning and soft-drop  etc. The focus was on preparation for Run II for which we expected up to 40 additional pileup events in comparison to Run I LHC data that had typically half the pileup events on average\\
{\bf Keywords}: Supersymmetry, gluino, scalar leptoquarks, pileup removal algorithms .

\end{singlespacing}


%\clearpage
\thispagestyle{empty}
\newpage

