\begin{thebibliography}{99}
%%%%%%%%%%%%%%%%%%% chapter-2 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{particle physics} F. Halzen and A. D. Martin, "Quarks and Leptons: An Introductory Course in Modern
Particle Physics".
\bibitem{sm} M.J.Herrero, "The Standard Model", {\url {http://arxiv.org/abs/hep-ph/9812242}}
\bibitem{higgs} P. W. Higgs, "Broken symmetries and the masses of gauge bosons", Phys. Rev. Lett. 13 (1964) 508 ; F. Englert and R. Brout, "Broken symmetries and the mass of gauge vector mesons", Phys.Rev. Lett. 13 (1964) 321.
\bibitem{collider-physics} Guido Altarelli, "Collider Physics within the Standard Model: a Primer", \url{http://arxiv.org/abs/1303.2842}
\bibitem{GSW} {J. Goldstone}, A. Salam, and S. Weinberg, Phys. Rev. 127, 965 (1962).
\bibitem{u1-collaboration1} G. Arnison {\it et al.} (UA1 Collaboration), Phys. Lett. B122 (1983) 103.
\bibitem{u1-collaboration2} G. Arnison {\it et al.} (UA1 Collaboration), Phys. Lett. B126 (1983) 398.
\bibitem{u2-collaboration1} M. Banner {\it et al.} (UA2 Collaboration), Phys. Lett. B122 (1983) 476.
\bibitem{u2-collaboration2} P. Bagnaia {\it et al.} (UA2 Collaboration), Phys. Lett.B129 (1983) 130. 
\bibitem{cdf-collab} F. Abe {\it et al.} (CDF Collaboration), Phys. Rev. Lett. 74 (1995) 2626.
\bibitem{do-collab}  S. Abachi {\it et al.} (D0 Collaboration), Phys. Rev. Lett. 74 (1995) 2632.
\bibitem{atlas-higgs} ATLAS Collaboration, "Observation of a new particle in the search for the Standard Model Higgs boson
with the ATLAS detector at the LHC", Physics Letters B 716 (2012) 1–29.
\bibitem{cms-higgs} CMS Collaboration, "Observation of a new boson at a mass of 125 GeV with the CMS experiment at
the LHC", Physics Letters B 716 (2012) 30–61.
\bibitem{pdg} J. Beringer {\it et al.} (Particle Data Group), "REVIEW OF PARTICLE PHYSICS", Phys. Rev. D86,010001 (2012).  DOI:\url{http://dx.doi.org/10.1103/PhysRevD.86.010001}.
\bibitem{tevnph-group} "Combined CDF and D0 Search for Standard Model Higgs Boson Production with up to 10.0 fb$^{−1}$ of Data". {\url{ http://arxiv.org/abs/1203.3774}}.
\bibitem {lep-group} "The LEP Electroweak Working Group", {\url {http://lepewwg.web.cern.ch/LEPEWWG/}}.
\bibitem{lhc-cross-section}  S. Dittmaier {\it et. al.} "Handbook of LHC Higgs Cross Sections: 2. Differential Distributions", \url{http://arxiv.org/abs/arXiv:1201.3084}. 
\bibitem{lhc-cross-section-working group} "LHC Higgs Cross Section Working Group (2012-2013)", {\url {https://twiki.cern.ch/twiki/bin/view/LHCPhysics/CrossSections}}.
\bibitem{bsm} A. Pomarol, "Beyond the Standard Model", CERN Yellow Report CERN-2012-001, pp. 115-151, \url{http://arxiv.org/abs/1202.1391}.
\bibitem{susy-book} J.Wess and J.Bagger, "Supersymmetry and Supergravity". Princeton Series in Physics.
\bibitem{extra-dim} T. Appelquist, H.C. Cheng, B.A. Dobrescu,“Bounds on Universal Extra Dimensions”, Phys. Rev. D64 035002 (2001).
\bibitem{hierarchy-prob} Nima Arkani-Hamed, Savas Dimopoulos, Gia Dvali, "The Hierarchy Problem and New Dimensions at a Millimeter", Phys.Lett.B429:263-272,1998, DOI: \url{{http://www.sciencedirect.com/science/article/pii/S0370269398004663}}, \url{http://arxiv.org/abs/hep-ph/9803315}.
\bibitem{mass hierarchy} L. Randall, R. Sundrum, "A Large Mass Hierarchy from a Small Extra Dimension", Phys. Rev. Lett. 83, 3370, \url{http://arxiv.org/abs/hep-ph/9905221}.
\bibitem{ferno} R. Fernow, Introduction to experimental particle physics.
\bibitem{D-green} D. Green, The Physics of Particle Detectors.
%%%%%%%%%%%%%%%%%%% chapter -3 %%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{lhc-design-report} "The LHC Design Report v.1", CERN-2004-003-V-1 {\url {http://cdsweb.cern.ch/record/782076}}
\bibitem{alice} ALICE Collaboration, "Technical Proposal for a Large Ion Collider Experiment at the CERN LHC", CERN-LHCC-95-71 (1995).
\bibitem {atlas}ATLAS Collaboration, "Detector and Physics Performance Technical Design Report, vol. 1",
CERN-LHCC-99-14 (1999).
\bibitem{cms-jinst} R. Adolphi {\it et al.} (CMS Collaboration), "The CMS experiment at the CERN LHC", JINST 0803:S08004, (2008).
\bibitem{lhc-b} LHCb Collaboration, "LHCb Technical Proposal", CERN-LHCC-98-04 (1998).
\bibitem{physics-tdr-8.1} CMS collaboration, "Physics Technical Design Report", Volume I : Detector Performance and software, CMS/LHCC 2006-001, CMS TDR 8.1.
\bibitem{physics-tdr-8.2} CMS collaboration, "Physics Technical Design Report", Volume II : Physics performance, CMS/LHCC 2006-021, CMS TDR 8.2.
\bibitem{cms-trigger} C. Seez, "The CMS trigger system", Eur Phys J C 34, s01, s151–s159 (2004).
\bibitem{cms-workbook} {\url{https://twiki.cern.ch/twiki/bin/view/CMSPublic/WorkBook}}
\bibitem{root} {\url{http://root.cern.ch/drupal/}}
%%%%%%%%%%%%%%%%%%%% chapter-4 %%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{calman-filtering} R. Fruhwirth, "Application of Kalman filtering to track and vertex fitting", Nucl. Instrum. Meth. A262 (1987) 444-450.
\bibitem {track and primary-vertex} CMS Collaboration, "Description and performance of track and primary-vertex reconstruction with the CMS tracker", CMS-TRK-11-001, \url{http://arxiv.org/abs/1405.6569}.
\bibitem {DA-algorithim} CMS Internal Note 14 (2011)
\bibitem{vertex filter} CMS Note 2007-008, 2007.
\bibitem{b-quark jet} CMS Collaboration, "Identification of b-quark jets with the CMS experiment", JINST 8 (2013) P04013,{\url{http://arxiv.org/abs/1211.4462}} DOI:{\url{http://iopscience.iop.org/1748-0221/8/04/P04013/}}.
\bibitem{muon-performance} CMS Collaboration, "Performance of muon identiﬁcation in pp collisions at $\sqrt {s}$ = 7 TeV". CMS-PAS-MUO-10-002.
\bibitem{cms-tdr} CMS/LHCC 2006-001, CMS TDR 8.1.
\bibitem{global-muon} G. Abbiendi et al., CMS AN-2008-097.
\bibitem{track-fitting} R. Fruhwirth, "Track fitting with non-Gaussian noise", Computer Physics Communications 100 (1997) 1–16. 
\bibitem{gsf-electron} W. Adam {\it et. al.}, Reconstruction of electrons with the gaussian-sum filter in the cms tracker at the lhc,CMS NOTE-2005/001.
\bibitem{electron-performance} "Electron performance with 19.6 $fb^{-1}$ of data collected at $\sqrt {s} $ = 8 TeV with the CMS detector.”, technical report, CERN, Geneva, Mar, 2013.
\bibitem{CS} M. Cacciari and G. P. Salam, "Pileup subtraction using jet areas", Phys.Lett. B659 (2008).
119–126, {\url{http://www.sciencedirect.com/science/article/pii/S0370269307011094}}, \url{http://arxiv.org/abs/0707.1378}.
\bibitem{jet-theory} S.D. Ellis {\it et. al.} "Jets in hadron–hadron collisions", Progress in Particle and Nuclear Physics 60 (2008) 484–551.
\bibitem{performance-jet alg} CMS Collaboration, "Performance of Jet Algorithms in CMS"; CMS-PAS-JME-07-003.
\bibitem{calo jet} V. Chetluru {\it et. al}; CMS-AN-2009/067.
\bibitem{track jet} CMS Collaboration, "Performance of Jet Reconstruction with Charged Tracks only", CMS-PAS-JME-08-001.
\bibitem{jpt jet}  CMS Collaboration, "Jet Plus Tracks Algorithm for Calorimeter Jet Energy Corrections in CMS." CMS-PAS-JME-09-002.
\bibitem{pflow jet} CMS Collaboration, "Particle–Flow Event Reconstruction in CMS and Performance for Jets, Taus, and $E_T^{miss}$", CMS-PAS-PFT-09-001.
\bibitem{jec}CMS Collaboration, “Determination of the jet energy scale in CMS with pp collisions at $\sqrt {s}$ = 7 TeV”, CMS-PAS JME-10-010 (2010)
\bibitem {missing energy} CMS Collaboration, "Missing transverse energy performance of the CMS detector", JINST 6 (2011) 09001, DOI: {\url{http://iopscience.iop.org/1748-0221/6/09/P09001/}}, {\url{http://arxiv.org/abs/1106.5048}}.
\bibitem {cms-an-12-366} B. Parida {\it et. al.} "Jet energy resolution with Z$\rightarrow(\mu^+\mu^-)$ + jet events at $\sqrt {s}$ = 7 TeV" CMS-AN-12-366.(2012)
%%%%%%%%%%%%%%%%%%%% chapter-5 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{fastjet} G. S. Matteo Cacciari and G. Soyez, "FastJet 2.3 User Manual", Phys. Lett. B 641:57 (2006)
\bibitem{kt-alg} S. Cataniand, Y. L. Dokshitzerand, M. H. Seymour, and B. R. Webber, "Longitudinally
invariant K(t) clustering algorithms for hadron hadron collisions," Nucl. Phys. B 406:187 (1993).
\bibitem {CSS} M. Cacciari, G. P. Salam, and G. Soyez, "The anti-$k_t$ jet clustering algorithm", JHEP 04
(2008) 063, DOI:{\url{http://iopscience.iop.org/1126-6708/2008/04/063/}}, \url{http://arxiv.org/abs/0802.1189}.
\bibitem {CA-alg.} {Y. L. Dokshitzer}, G. Leder, S. Moretti, and B. Webber, "Better jet clustering algorithms",
JHEP 9708 (1997) 001, \url{http://arxiv.org/abs/hep-ph/9707323}.
\bibitem{sucssesive jet alg} S. D. Ellis and D. E. Soper, "Successive combination jet algorithm for hadron collisions", Phys.
Rev. D 48 3160 (1993).
\bibitem{grooming} S.D. Ellis, C.K. Vermilion and J.R. Walsh, "Techniques for improved heavy particle searches
with jet substructure", Phys. Rev. D 80 (2009) 051501, \url{http://arxiv.org/abs/0903.5081}. 
\bibitem {filtering} J. M. Butterworth {\it et al.}, "Jet substructure as a new Higgs-search channel at the LHC",
Phys. Rev. Lett. 100 (2008) 242001, DOI: {\url{http://dx.doi.org/10.1103/PhysRevLett.100.242001}}, \url{http://arxiv.org/abs/0802.2470}.
\bibitem {trimming} D. Krohn, J. Thaler, and L.-T. Wang, "Jet Trimming", JHEP 02 (2010) 084, {\url{http://arxiv.org/abs/0912.1342}}.
\bibitem {pruning} S. D. Ellis, C. K. Vermilion, and J. R. Walsh, "Recombination Algorithms and Jet
Substructure: Pruning as a Tool for Heavy Particle Searches", Phys. Rev. D 81 (2010) 094023, DOI: {\url{http://dx.doi.org/10.1103/PhysRevD.81.094023}}, \url{http://arxiv.org/abs/0912.0033}.
\bibitem{softdrop} A. J. Larkoski, S. Marzani, G. Soyez, and J. Thaler, "Soft Drop", JHEP 1405 (2014) 146, \url{http://arxiv.org/abs/1402.2657}.
\bibitem {DFMS-mmdt} M. Dasgupta, A. Fregoso, S. Marzani, and G. P. Salam, "Towards an understanding of jet
substructure", JHEP 1309 (2013) 029, \url{http://arxiv.org/abs/1307.0007}.
\bibitem {BDRS} J. M. Butterworth, A. R. Davison, M. Rubin, and G. P. Salam, "Jet substructure as a new
Higgs search channel at the LHC", \url{http://arxiv.org/abs/0810.0409}.
\bibitem{w-tag-theory} Y. Cui, Z. Han, and M. D. Schwartz, "W-jet Tagging: Optimizing the Identification of Boosted Hadronically-Decaying W Bosons", Phys.Rev. D83 (2011), \url{http://arxiv.org/abs/1012.2077}.
\bibitem {TV} J. Thaler and K. Van Tilburg, "Identifying Boosted Objects with N-subjettiness", JHEP 1103 (2011) 015, doi:10.1007/JHEP03(2011)015, {\url{http://arxiv.org/abs/1011.2268}}.
\bibitem{q-jet} S. D. Ellis $\it et al.$, "Qjets: A Non-Deterministic Approach to Tree-Based Jet Substructure", Phys.Rev.Lett. 108 (2012) 182003, doi:10.1103/PhysRevLett.108.182003, \url{http://arxiv.org/abs/1201.1914}.
%%%%%%%%%5%%%%%%  chapter-6 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{an-12-381} Searches for new physics in the $WW\rightarrow \ell\nu j$ final state with merged W bosons". CMS-AN-12-381
\bibitem{hig-13-008}CMS Collaboration, "Search for a Standard Model-like Higgs boson decaying into $WW\rightarrow \nu q\bar q^{\prime}$ in pp collisions at $\sqrt {s}$ = 8 TeV", CMS-PAS-HIG-13-008 (2013).
\bibitem{an-13-414} Semi-leptonic decay of HWW at high mass in exclusive jet bins. CMS-AN-13-414 (2014)
\bibitem{hig-14-008} CMS Collaboration, "Search for a Standard Model Higgs-like boson decaying into $WW\rightarrow \nu q\bar q^{\prime}$ in exclusive jet bins in pp collisions at $\sqrt {s}$ = 8 TeV", CMS-PAS-HIG-14-008.
\bibitem{group-pattuple}  {\url {https://twiki.cern.ch/twiki/bin/view/CMS/HiggsWWTolnujjCommonPATtuples}}.
\bibitem{gsf electron} CMS Collaboration, "Electron Reconstruction and Selection Studies with First CMS 7
TeV Data", CMS-PAS-EGM-10-004 (2010).
\bibitem{muon identification} CMS Collaboration, "Performance of CMS muon identification in pp collisions at $\sqrt {s}$ = 7 TeV", CMS PAS MUO-2010-002(2010).
\bibitem {met performance} CMS Collaboration, "CMS MET Performance in Events Containing Electroweak Bosons from pp Collisions at $\sqrt s$= 7 TeV". CMS-PAS-JME-10-005
\bibitem{pflow} CMS Collaboration, "Particle-Flow Event Reconstruction in CMS and Performance for Jets, Taus, and MET”, CMS PAS PFT-2009-001 (Apr, 2009).
\bibitem {particle flow reconstruction} CMS Collaboration, "Commissioning of the Particle-Flow Reconstruction in
Minimum-Bias and Jet Events from pp Collisions at 7 TeV", CMS-PAS-PFT-2010-002 (2010).
\bibitem{jet performance} CMS Collaboration, "Jet Performance in pp Collisions at $\sqrt s$=7 TeV", CMS-PAS-JME-10-003, (2010).
\bibitem {jet id}  CMS Collaboration, "Jet identification in high pile-up environment", CMS twiki
PileupJetID twiki (2012) {\url {https://twiki.cern.ch/twiki/bin/viewauth/CMS/PileupJetID}}
\bibitem{cms-an-12-029} A. Benaglia, L. Di Matteo, and P. Govoni, "Search for Higgs Boson Decays into Two W
Bosons in the Semi-leptonic Final State with the Full 2011 pp Dataset at $\sqrt{s}$ = 7 TeV.", CMS-AN-12-029 (2012).
\bibitem{cms-an-12-021} N. Akchurin {\it et al.}, "Computation of Offline and Trigger Efficiencies for Standard Model
Higgs boson search in $\rm H\rightarrow WW\rightarrow \ell\nu jj$ decay", CMS-AN-12-021 (2012).
\bibitem{massive resonance} CMS Collaboration, "Search for massive resonances decaying into pairs of
boosted bosons in semi-leptonic final states at $\sqrt{s}$= 8 TeV", \url{http://arxiv.org/abs/1405.3447}.
\bibitem{w-tag} {CMS Collaboration}, "Identifying Hadronically Decaying Vector Bosons Merged into a
Single Jet",CMS-PAS-JME-13-006 (2013).
\bibitem{dijet mass} {CMS Collaboration}, "Studies of jet mass in dijet and W/Z + jet events",
JHEP 1305 (2013) 090, doi:10.1007/JHEP05(2013)090, \url{http://arxiv.org/abs/1303.4811}.
\bibitem{b-jet} {CMS Collaboration}, "b-Jet Identification in the CMS Experiment”, CMS-PAS-BTV-11-004,(2012).
\bibitem {smp-12-019} CMS Collaboration, PAS SMP-12-019 (2012).
\bibitem {diboson production} CMS Collaboration, “Measurement of $W^+W^-$ and ZZ production cross
sections in pp collisions at $\sqrt{s}$ = 8 TeV”, Phys.Lett. B721 (2013) 190–211,
doi:10.1016/j.physletb.2013.03.027, \url{http://arxiv.org/abs/1301.4698}.
\bibitem{higgs-cross section} LHC Higgs Cross Section Working Group Collaboration, "Handbook of LHC Higgs
Cross Sections: 3. Higgs Properties", doi:10.5170/CERN-2013-004, \url{http://arxiv.org/abs/1307.1347}.
\bibitem{CLs} CLs "Procedure for the LHC Higgs boson search combination in summer 2011", ATL-PHYS-PUB-2011-011, CMS NOTE-2011/005 (Aug, 2011).
\bibitem{cLs} {A. L. Read}, "Presentation of search results: the CLs technique", Journal of Physics G: Nuclear and Particle Physics 28 (2002), no. 10, 2693.
\bibitem{lumi} CMS Collaboration, "CMS Luminosity Based on Pixel Cluster Counting – Summer 2013 Update", CMS-PAS-LUM-13-001 (2013).
\bibitem{vv-scattering} {A. Ballestrero}, G. Bevilacqua, D. B. Franzosi, and E. Maina, “How well can the LHC
distinguish between the SM light Higgs scenario, a composite Higgs and the Higgsless
case using VV scattering channels?”, JHEP 11 (2009) 126,
doi:10.1088/1126-6708/2009/11/126, \url{http://arxiv.org/abs/0909.3838}.
%%%%%%%%%%%%%%%%% chapter-7 %%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{pileup AN} Study of Pileup Removal Algorithms for Jets, CMS-AN-14-175. (2014)
\bibitem{pileup removal alg.} Study of Pileup Removal Algorithms for Jets, CMS-PAS JME-14-001. (2014)
\bibitem {S} G. Soyez {\it et al}., "Pileup subtraction for jet shapes", Phys.Rev.Lett. 110 (2013), no. 16, 162001, doi:10.1103/PhysRevLett.110.162001, \url{http://arxiv.org/abs/1211.2811}
\bibitem {EVW} S. D. Ellis, C. K. Vermilion, and J. R. Walsh, "Techniques for improved heavy particle
searches with jet substructure", Phys. Rev. D 80 (2009) 051501, doi:10.1103/PhysRevD.80.051501, \url{http://arxiv.org/abs/0903.5081}.
\bibitem {safe subtraction} M. Cacciari, G. P. Salam, and G. Soyez, "On the use of charged-track information to subtract neutral pileup", \url{http://arxiv.org/abs/1404.7353}.
\bibitem{cleansing} D. Krohn, M. Schwartz, M. Low, and L.-T. Wang, "Jet Cleansing: Pileup Removal at High
Luminosity", \url{http://arxiv.org/abs/1309.4777}.
\bibitem{puppi} D. Bertolini, P. Harris, M. Low, and N. Tran, "Pileup Per Particle Identification", \url{http://arxiv.org/abs/1407.6013}.

\end{thebibliography}
