\begin{thebibliography}{99}
\onehalfspacing
%%%%%%%Synopsis and chap1%%%%%%%%%%%%%%%
\bibitem{SUSYtheo}
H.~Nilles, ``{Supersymmetry, supergravity and particle physics},''
  \href{http://dx.doi.org/10.1016/0370-1573(84)90008-5}{{\em Phys. Rep.}
  {\bfseries 110} (1984) 1}.


\bibitem{guts}
H.~Georgi and S.~Glashow.
\newblock Unity of all elementary-particle forces.
\newblock {\em Phys. Rev. Lett.}, 32:438, 1974.

\bibitem{RParity}
G.~Farrar and P.~Fayet, ``{Phenomenology of the production, decay, and
  detection of new hadronic states associated with supersymmetry},''
  \href{http://dx.doi.org/10.1016/0370-2693(78)90858-4}{{\em Phys. Lett. B}
  {\bfseries 76} (1978) 575}.

\bibitem{Naturaln}
G.~G. S.~Dimopoulos, ``{Naturalness constraints in supersymmetric theories with
  nonuniversal soft terms},''
  \href{http://dx.doi.org/10.1016/0370-2693(95)00961-J}{{\em Phys. Lett. B}
  {\bfseries 357} (1995) 573}.

\bibitem{SMS1}
P.~S. Alwall and N.~Toro, ``{Simplified models for a first characterization of
  new physics at the LHC},''
  \href{http://dx.doi.org/10.1103/PhysRevD.79.075020}{{\em Phys. Rev. D}
  {\bfseries 79} (2009) 075020}.


\bibitem{LQ1}
B.~Schrempp and F.~Schremp, ``{Light Leptoquark},''
  \href{http://dx.doi.org/10.1016/0370-2693(85)91450-9}{{\em Phys. Lett. B}
  {\bfseries 153} (1985) 101}.

\bibitem{LQ2}
S.~Dimopoulos and L.~Susskind, ``{Mass Without Scalar},''
  \href{http://dx.doi.org/10.1016/0550-3213(81)90304-7}{{\em Nucl. Phys. B}
  {\bfseries 155} (1979) 237}.

\bibitem{LQ3}
J.~C. Pati and A.~Salam, ``{Lepton Number as the Fourth Color},''
  \href{http://dx.doi.org/10.1103/PhysRevD.10.275}{{\em Phys. Rev. D}
  {\bfseries 10} (1974) 275}.

\bibitem{LQ4}
W.~Buchmuller and D.~Wyler, ``{Constraints on SU(5) Type Leptoquarks},''
\href{http://dx.doi.org/10.1016/0370-2693(86)90771-9}{{\em Phys. Lett.}
  {\bfseries B177} (1986) 377--382}.
%%CITATION = PHLTA,B177,377;%%.

\bibitem{guts}
H.~Georgi and S.~Glashow.
\newblock Unity of all elementary-particle forces.
\newblock {\em Phys. Rev. Lett.}, 32:438, 1974.


\bibitem{composite}
B.~Schrempp and F.~Schrempp.
\newblock Light leptoquarks.
\newblock {\em Phys. Lett. B}, 153:101, 1985.

\bibitem{technicolor2}
S.~Dimopoulos.
\newblock Technicolored signatures.
\newblock {\em Nucl. Phys. B}, 168:69, 1980.


\bibitem{technicolor3}
E.~Eichten and K.~Lane.
\newblock Dynamical breaking of the weak interaction symmetries.
\newblock {\em Phys. Lett. B}, 90:85, 1980.


\bibitem{superstring_e6}
J.~L. Hewett and T.~G. Rizzo.
\newblock {Low-energy phenomenology of superstring-inspired E$_{6}$ models}.
\newblock {\em Phys. Lett.}, 183:193, 1989.







\bibitem{cms}
{\bfseries CMS} Collaboration, S.~Chatrchyan {\em et~al.}, ``{The CMS
  experiment at the CERN LHC},''
\href{http://dx.doi.org/10.1088/1748-0221/3/08/S08004}{{\em JINST} {\bfseries
  3} (2008) S08004}.
%%CITATION = JINST,3,S08004;%%.

\bibitem{Beaudette:2014cea}
{\bfseries CMS} Collaboration, F.~Beaudette, ``{The CMS Particle Flow
  Algorithm},'' in {\em {Proceedings, International Conference on Calorimetry
  for the High Energy Frontier (CHEF 2013): Paris, France, April 22-25, 2013}},
  pp.~295--304.
\newblock 2013.
\newblock \href{http://arxiv.org/abs/1401.8155}{{\ttfamily arXiv:1401.8155
  [hep-ex]}}.
\newblock
\url{https://inspirehep.net/record/1279774/files/arXiv:1401.8155.pdf}.
\newblock
%%CITATION = ARXIV:1401.8155;%%.

\bibitem{Cacciari:2008gp}
M.~Cacciari, G.~P. Salam, and G.~Soyez, ``{The Anti-k(t) jet clustering
  algorithm},'' \href{http://dx.doi.org/10.1088/1126-6708/2008/04/063}{{\em
  JHEP} {\bfseries 04} (2008) 063},
\href{http://arxiv.org/abs/0802.1189}{{\ttfamily arXiv:0802.1189 [hep-ph]}}.
%%CITATION = ARXIV:0802.1189;%%.

\bibitem{CMS-NOTE-2011-005}
{\bfseries The ATLAS Collaboration, The CMS Collaboration, The LHC Higgs
  Combination Group} Collaboration, ``{Procedure for the LHC Higgs boson search
  combination in Summer 2011},'' Tech. Rep. CMS-NOTE-2011-005.
  ATL-PHYS-PUB-2011-11, CERN, Geneva, Aug, 2011.
\newblock \url{https://cds.cern.ch/record/1379837}.

\bibitem{CMS-PAS-SUS-15-002}
{\bfseries CMS} Collaboration, ``{Search for supersymmetry in the multijet and
  missing transverse momentum channel in pp collisions at 13 TeV},'' Tech. Rep.
  CMS-PAS-SUS-15-002, CERN, Geneva, 2015.
\newblock \url{https://cds.cern.ch/record/2114817}.

\bibitem{CMS-PAS-SUS-16-014}
{\bfseries CMS} Collaboration, ``{Search for supersymmetry in events with jets
  and missing transverse momentum in proton-proton collisions at 13 TeV},''
  Tech. Rep. CMS-PAS-SUS-16-014, CERN, Geneva, 2016.
\newblock \url{https://cds.cern.ch/record/2205158}.

\bibitem{CMS-PAS-EXO-16-043}
{\bfseries CMS} Collaboration, ``{Search for pair-production of first
  generation scalar leptoquarks in pp collisions at $\sqrt{s}=13~\mathrm{TeV}$
  with $2.6~\mathrm{fb}^{-1}$},'' Tech. Rep. CMS-PAS-EXO-16-043, CERN, Geneva,
  2016.
\newblock \url{https://cds.cern.ch/record/2205285}.

\bibitem{CMS-PAS-EXO-12-041}
{\bfseries CMS} Collaboration, ``{Search for Pair-production of First
  Generation Scalar Leptoquarks in pp Collisions at sqrt s = 8 TeV},'' Tech.
  Rep. CMS-PAS-EXO-12-041, CERN, Geneva, 2014.
\newblock \url{https://cds.cern.ch/record/1742179}.

\bibitem{Grooming}
J.~M. Butterworth, A.~R. Davison, M.~Rubin, and G.~P. Salam, ``{Jet
  substructure as a new Higgs search channel at the LHC},''
  \href{http://dx.doi.org/10.1103/PhysRevLett.100.242001}{{\em Phys. Rev.
  Lett.} {\bfseries 100} (2008) 242001}.

\bibitem{Ellis:2009me}
S.~D. Ellis, C.~K. Vermilion, and J.~R. Walsh, ``{Recombination Algorithms and
  Jet Substructure: Pruning as a Tool for Heavy Particle Searches},''
  \href{http://dx.doi.org/10.1103/PhysRevD.81.094023}{{\em Phys. Rev.}
  {\bfseries D81} (2010) 094023}.

\bibitem{Dasgupta:2013ihk}
M.~Dasgupta, A.~Fregoso, S.~Marzani, and G.~P. Salam, ``{Towards an
  understanding of jet substructure},''
  \href{http://dx.doi.org/10.1007/JHEP09(2013)029}{{\em JHEP} {\bfseries 09}
  (2013) 029}.

\bibitem{Krohn:2009th}
D.~Krohn, J.~Thaler, and L.-T. Wang, ``{Jet Trimming},''
  \href{http://dx.doi.org/10.1007/JHEP02(2010)084}{{\em JHEP} {\bfseries 02}
  (2010) 084}.

\bibitem{Larkoski:2014wba}
A.~J. Larkoski, S.~Marzani, G.~Soyez, and J.~Thaler, ``{Soft Drop},''
  \href{http://dx.doi.org/10.1007/JHEP05(2014)146}{{\em JHEP} {\bfseries 05}
  (2014) 146}.

\bibitem{JMEPAS}
{\bfseries CMS} Collaboration, ``{Study of Pileup Removal Algorithms for Jets
  },'' Tech. Rep. CMS-PAS-JME-14-001, CERN, Geneva, 2016.
\newblock \url{https://cds.cern.ch/record/1751454}.


\bibitem{MuonPOG}
{\bfseries CMS} Collaboration, ``{Muon Physics Object Group},''
\newblock \url{https://twiki.cern.ch/twiki/bin/viewauth/CMS/MuonPOG}


\bibitem{ElectronPOG}
{\bfseries CMS} Collaboration, ``{E/gamma Physics Object Group},''
\newblock \url{https://twiki.cern.ch/twiki/bin/view/CMS/CutBasedElectronIdentificationRun2}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%synopsis and chap1%%%%%%%%%%%%%%%%%%%%%%
\bibitem{APichSM}
Antonio Pich.
\newblock {The Standard model of electroweak interactions}.
\newblock In {\em {High-energy physics. Proceedings, European School,
  Aronsborg, Sweden, June 18-July 1, 2006}}, pages 1--49, 2007.
\newblock [,1(2007)].

\bibitem{particle physics} F. Halzen and A. D. Martin, ``Quarks and Leptons: An Introductory Course in Modern
Particle Physics''.
\bibitem{sm} M. J. Herrero, ``The Standard Model'', {\url {http://arxiv.org/abs/hep-ph/9812242}}.

\bibitem{atlas-higgs} ATLAS Collaboration, ``Observation of a new particle in the search for the Standard Model Higgs boson
with the ATLAS detector at the LHC'', Physics Letters B 716 (2012) 1–29.
\bibitem{cms-higgs} CMS Collaboration, ``Observation of a new boson at a mass of 125 GeV with the CMS experiment at
the LHC'', Physics Letters B 716 (2012) 30–61.

\bibitem{SMandParticles} Wikipedia ``Standard Model'' {\url{https://en.wikipedia.org/wiki/Standard_Model}}.

\bibitem{APichQCD}
Antonio Pich.
\newblock {Quantum chromodynamics}.
\newblock (hep-ph/9505231. FTUV-95-19. IFIC-95-19):51 p, May 1995.




\bibitem{Quark1}
E.~D. Bloom, D.~H. Coward, H.~DeStaebler, J.~Drees, G.~Miller, L.~W. Mo, R.~E.
  Taylor, M.~Breidenbach, J.~I. Friedman, G.~C. Hartmann, and H.~W. Kendall.
\newblock High-energy inelastic $e{-}p$ scattering at $6^{0}$ and $10^{0} $.
\newblock {\em Phys. Rev. Lett.}, 23:930--934, Oct 1969.



\bibitem{Quark2}
M.~Breidenbach, J.~I. Friedman, H.~W. Kendall, E.~D. Bloom, D.~H. Coward,
  H.~DeStaebler, J.~Drees, L.~W. Mo, and R.~E. Taylor.
\newblock Observed behavior of highly inelastic electron-proton scattering.
\newblock {\em Phys. Rev. Lett.}, 23:935--939, Oct 1969.



\bibitem{Gluon}
W.~Bartel, T.~Canzler, D.~Cords, P.~Dittmann, R.~Eichler, R.~Felst, D.~Haidt,
  S.~Kawabata, H.~Krehbiel, B.~Naroska, L.H. O'Neill, J.~Olsson, P.~Steffen,
  W.L. Yen, E.~Elsen, M.~Helm, A.~Petersen, P.~Warming, G.~Weber, H.~Drumm,
  J.~Heintze, G.~Heinzelmann, R.D. Heuer, J.~von Krogh, P.~Lennert,
  H.~Matsumura, T.~Nozaki, H.~Rieseberg, A.~Wagner, D.C. Darvill, F.~Foster,
  G.~Hughes, H.~Wriedt, J.~Allison, J.~Armitage, I.~Duerdoth, J.~Hassard,
  F.~Loebinger, B.~King, A.~Macbeth, H.~Mills, P.G. Murphy, H.~Prosper,
  K.~Stephens, D.~Clarke, M.C. Goddard, R.~Hedgecock, R.~Marshall, G.F. Pearce,
  M.~Imori, T.~Kobayashi, S.~Komamiya, M.~Koshiba, M.~Minowa, S.~Orito,
  A.~Sato, T.~Suda, H.~Takeda, Y.~Totsuka, Y.~Watanabe, S.~Yamada, and
  C.~Yanagisawa.
\newblock Observation of planar three-jet events in e+e− annihilation and
  evidence for gluon bremsstrahlung.
\newblock {\em Physics Letters B}, 91(1):142 -- 147, 1980.



\bibitem{topquark}
Frank Fiedler.
\newblock {Top quark production and properties at the Tevatron}.
\newblock In {\em {Les Rencontres de physique de la Vall'ee d'Aoste, results
  and perspectives in particle physics, La Thuile, Aoste Valley, February 27 -
  March 5, 2005}}, pages 503--520, 2005.


\bibitem{AsympQCD1} David J. Gross and Frank Wilczek,``Ultraviolet Behavior of Non-Abelian Gauge Theories", Phys. Rev. Lett. 30 (1973) 1343.

\bibitem{AsympQCD2} H. David Politzer,``Reliable Perturbative Results for Strong Interactions?", Phys. Rev. Lett. 30 (1973) 1346.

\bibitem{GSW} {J. Goldstone}, A. Salam, and S. Weinberg, Phys. Rev. 127, 965 (1962).


\bibitem{higgs} P. W. Higgs, ``Broken symmetries and the masses of gauge bosons", Phys. Rev. Lett. 13 (1964) 508 ; F. Englert and R. Brout, ``Broken symmetries and the mass of gauge vector mesons'', Phys.Rev. Lett. 13 (1964) 321.


\bibitem{WZbosonMass1}  ``The  LEP  Collaborations  ALEPH,  DELPHI,  L3  and  OPAL  and  the  LEP  Electroweak  Working Group'', \url{http://arxiv.org/abs/hep-ex/0612034}.

\bibitem{WZbosonMass2} ``The ALEPH, DELPHI, L3, OPAL and SLD Collaborations, the LEP Electroweak Working Group and the SLD Electroweak and Heavy Flavour Group'', Phys. Rept. 427 (2006) 257.

\bibitem{TopQuarkMass}  (ATLAS, CDF, CMS, D0 Collaborations),P. A. R. Ade{\it et al.}``First combination of Tevatron and LHC measurements of the top-quak mass'', \url{https://arxiv.org/abs/1403.4427}.

\bibitem{DarkMatter}  (Planck Collaboration)``Planck 2013 results. XVI Cosmological parameters'', \url{https://arxiv.org/abs/1303.5076}.


\bibitem{bsm} A. Pomarol, ``Beyond the Standard Model'', CERN Yellow Report CERN-2012-001, pp. 115-151, \url{http://arxiv.org/abs/1202.1391}.


\bibitem{SUSYprimer}
Stephen~P. Martin.
\newblock {A Supersymmetry primer}.
\newblock 1997.
\newblock [Adv. Ser. Direct. High Energy Phys.18,1(1998)].




\bibitem{MSSMref}
Csaba Csaki.
\newblock {The Minimal supersymmetric standard model (MSSM)}.
\newblock {\em Mod. Phys. Lett.}, A11:599, 1996.


\bibitem{NMSSMref}
Pierre Fayet.
\newblock {Supergauge Invariant Extension of the Higgs Mechanism and a Model
  for the electron and Its Neutrino}.
\newblock {\em Nucl. Phys.}, B90:104--124, 1975.


\bibitem{extra-dim} T. Appelquist, H. C. Cheng, B. A. Dobrescu, ``Bounds on Universal Extra Dimensions'', Phys. Rev. D64 035002 (2001).




\bibitem{LQLHC} Jason L. Evans, Natsumi Nagata, ``Signatures of Leptoquarks at the LHC
and Right-handed Neutrinos'', {\url {https://arxiv.org/pdf/1505.00513.pdf}}.


\bibitem{pdg1} K. Olive {\it et al.} (Particle Data Group), ``Review of Particle Physics'', Chin. Phys. C38,(2014)090001.


\bibitem{cms-jinst} R. Adolphi {\it et al.} (CMS Collaboration), ``The CMS experiment at the CERN LHC'', JINST 0803:S08004, (2008).

\bibitem{physics-tdr-8.1} CMS collaboration, ``Physics Technical Design Report'', Volume I : Detector Performance and software, CMS/LHCC 2006-001, CMS TDR 8.1.
\bibitem{physics-tdr-8.2} CMS collaboration, ``Physics Technical Design Report'', Volume II : Physics performance, CMS/LHCC 2006-021, CMS TDR 8.2.



\bibitem{cms-det} CMS Collaboration, ``Recent Results of the CMS Experiment'', \url{https://inspirehep.net/record/1193345/files/cms.png}.

\bibitem{theLHC} The Large Hadron Collider, ``The Large Hadron Collider'', \url{http://home.cern/topics/large-hadron-collider}.

\bibitem{xsecGlu} LHC SUSY Cross Section Working Group , ``SUSY Cross Sections'', \url{https://twiki.cern.ch/twiki/bin/view/LHCPhysics/SUSYCrossSections}.

\bibitem{PValgo} E. Chabanat and N. Estre , ``Deterministic annealing for vertex finding at CMS'', \url{http://dx.doi.org/10.5170/CERN-2005-002.287}.


\bibitem{GSF} {\bf CMS} Collaboration ,``Electromagnetic Physics Objects Commisioning with first LHC data'', \url{http://dx.doi.org/10.5170/CERN-2005-002.287}.


\bibitem {PFmethod} CMS Collaboration, ``Commissioning of the Particle-Flow Reconstruction in
Minimum-Bias and Jet Events from pp Collisions at 7 TeV'', CMS-PAS-PFT-2010-002 (2010).


\bibitem {antiKT} M. Cacciari, G. P. Salam, and G. Soyez, ``The anti-$k_t$ jet clustering algorithm'', JHEP 04
(2008) 063, \url{http://arxiv.org/abs/0802.1189}.

\bibitem {MuonReco} CMS Collaboration, S.Chatrchyan {\it et al} ``Performance of CMS Muon reconstruction in pp collision events at $\sqrt{s}$= 7 TeV '', JINST 7 (2012) P10002, \url{http://arxiv.org/abs/1206.4071}.



\bibitem{Butterworth:2008tr}
Jonathan~M. Butterworth, Adam~R. Davison, Mathieu Rubin, and Gavin~P. Salam.
\newblock {Jet substructure as a new Higgs search channel at the LHC}.
\newblock 2008.


\bibitem{Dokshitzer:1997in}
Yuri~L. Dokshitzer, G.D. Leder, S.~Moretti, and B.R. Webber.
\newblock {Better jet clustering algorithms}.
\newblock {\em JHEP}, 9708:001, 1997.



\bibitem{Cacciari:2014jta}
Matteo Cacciari, Gavin~P. Salam, and Gregory Soyez.
\newblock {On the use of charged-track information to subtract neutral pileup}.
\newblock 2014.




\bibitem{SUSYhad8TeV}
Chatrchyan {\rm et. al}.
\newblock {Search for new physics in the multijet and missing transverse
  momentum final state in proton-proton collisions at $\sqrt{s}$ = 8 TeV}.
\newblock {\em J. High Energy Phys.}, 06(arXiv:1402.4770. CMS-SUS-13-012.
  CERN-PH-EP-2014-015):055. 37 p, Feb 2014.
\newblock Comments: Replaced with published version. Added journal reference
  and DOI.





\bibitem{CMSSUSPublic} CMS Collaboration , ``https://twiki.cern.ch/twiki/bin/view/CMSPublic/PhysicsResultsSUS '', \url{https://twiki.cern.ch/twiki/bin/view/CMSPublic/SUSYSMSSummaryPlots8TeV}.





\bibitem{atlasLQ8TeVpaper}
Georges Aad et~al.
\newblock {Searches for scalar leptoquarks in pp collisions at ${\sqrt{s}}$ = 8
  TeV with the ATLAS detector}.
\newblock {\em Eur. Phys. J.}, C76(1):5, 2016.




\bibitem{PunziSignificance}
Giovanni Punzi.
\newblock {Sensitivity of searches for new signals and its optimization}.
\newblock {\em eConf}, C030908:MODT002, 2003.
\newblock [,79(2003)].


\bibitem{PruningPic}
Marco Peruzzi.
\newblock {Jet and photon physics}.
\newblock In {\em {Proceedings, 2nd Conference on Large Hadron Collider Physics
  Conference (LHCP 2014): New York, USA, June 2-7, 2014}}, 2014.



\bibitem{ktalgo} S. Cataniand, Y. L. Dokshitzerand, M. H. Seymour, and B. R. Webber, ``Longitudinally
invariant $k_{t}$ clustering algorithms for hadron hadron collisions,'' Nucl. Phys. B 406:187 (1993).

\end{thebibliography}
