%\thispagestyle{empty}
\begin{center}
{\large {\underline{\bf PUBLICATIONS}}}
\vskip 0.5cm
\end{center}
\begin{singlespacing}
{\large{\underline {\bf CMS Analysis Notes}}}
\begin{itemize}
\item[1.]{\bf {B. Parida}}, G.B. Mohanty, T. Aziz {\it et al.} ``Study of Pileup Algorithms for Jets'', \href{http://cms.cern.ch/iCMS/jsp/openfile.jsp?tp=draft&files=AN2014_175_v3.pdf} {CMS-AN-2014-175}.

\item[2.]{\bf {B. Parida}}, G.B. Mohanty, T. Aziz {\it et al.} ``Semi-leptonic decay of HWW at high mass in exclusive jet bins'', \href {http://cms.cern.ch/iCMS/jsp/openfile.jsp?tp=draft&files=AN2013_414_v12.pdf}{CMS-AN-2013-414}.

\item[3.]{\bf{B. Parida}}, G.B. Mohanty, T. Aziz {\it et al.} ``Search for high mass exotic resonances decaying to $\rm WW$ in the semi-leptonic channel'', \href{http://cms.cern.ch/iCMS/jsp/openfile.jsp?tp=draft&files=AN2013_139_v10.pdf}{CMS-AN-2013-139}.
\item[4.]{\bf{B. Parida}}, G.B. Mohanty, T. Aziz {\it et al.} ``Measurement of the electroweak production cross section of a $\rm W$ boson with two jets in pp collisions at $\sqrt{s}$ = 8 TeV'', \href{http://cms.cern.ch/iCMS/jsp/openfile.jsp?tp=draft&files=AN2013_123_v4.pdf} {CMS-AN-2013-123}.

\item[5.]{\bf {B. Parida}}, G.B. Mohanty, T. Aziz {\it et al.} ``Searches for new physics in the $\rm WW\rightarrow\ell\nu j$ final state with hadronic $\rm W$ bosons merged into a single jet'', \href{http://cms.cern.ch/iCMS/jsp/openfile.jsp?tp=draft&files=AN2012_381_v7.pdf} {CMS-AN-2012-381}.

\item[6.]{\bf {B. Parida}}, A. Nikitenko, G.B. Mohanty, A. Nayak and T. Aziz, ``Jet energy resolution with  Z($\rightarrow\mu^{+}\mu^{-})$ + jet events at $\sqrt{s}$ = 7 TeV'', \href {http://cms.cern.ch/iCMS/jsp/openfile.jsp?tp=draft&files=AN2012_366_v2.pdf} {CMS-AN-2012-366}.
\end{itemize}
{\large{\underline {\bf CMS Physics Analysis Summaries}}}
\begin{itemize}
\item[1.] CMS Collaboration,``Study of Pileup Removal Algorithms for Jets'', \href{https://cds.cern.ch/record/1751454}{CMS-PAS-JME-14-001}.
\item[2.] CMS Collaboration, ``Search for a Standard Model Higgs-like boson decaying into $\rm WW\rightarrow \ell\nu q\bar{q}^\prime$ in exclusive jet bins in pp collisions at $\sqrt {s}$ = 8 TeV'', \href{http://cms.cern.ch/iCMS/analysisadmin/versions?analysis=HIG-14-008} {CMS-PAS-HIG-14-008}.
\item[3.] CMS Collaboration, ``Search for a Standard Model-like Higgs boson decaying into $\rm WW\rightarrow\ell\nu q\bar{q}^\prime$ in pp collisions at $\sqrt{s}$ = 8 TeV'', \href{https://cds.cern.ch/record/1546778?ln=en} {CMS-PAS-HIG-13-008}.
\item[4.] CMS Collaboration,``Search for a Standard Model-like Higgs boson decaying to WW or ZZ in the mass range 145 to 1000 GeV at the LHC Run I'', \href{http://cms.cern.ch/iCMS/analysisadmin/versions?analysis=HIG-13-031} {CMS-PAS-HIG-13-031} (High Mass Legacy Paper).
\item[5.] CMS Collaboration, ``Search for new resonances decaying to $\rm WW\rightarrow \ell\nu q\bar{q}^\prime$ in the final state with a lepton, missing transverse energy and single reconstructed jet'',  \href{http://cds.cern.ch/record/1590301?ln=en}{CMS-PAS-EXO-12-021}.
\item[6.] CMS Collaboration, ``Measurement of the cross section of the electroweak production of a W boson with two jets in pp collisions at $\sqrt{s}$ = 8 TeV'', \href{http://cms.cern.ch/iCMS/analysisadmin/versions?analysis=SMP-13-012} {CMS-PAS-SMP-13-012}.
\end{itemize}
{\large{\underline {\bf Phenomenology}}}
\begin{itemize}
\item[1.] {\bf {B. Parida}}, S.N. Nayak {\it et al.}, ``Meson spectra in p + p collisions at LHC'', Indian Journal of Science and Technology; Vol.6(9); ISSN 0974-6846; Sep 2013; p. 5277-5280.
\end{itemize}
Besides above publications, I am a coauthor of all publications of the CMS Collaboration starting from 2011 (at present 280 publications). All can be found in \url{http://inspirehep.net/search?ln=en&ln=en&p=B+Parida+CMS+experiment}.
\end{singlespacing}






























